Paper Plots V2

### 2025-02-26 Rmd/paper_plots/paper_plots_1.2.Rmd
update paper plots and run 500 iters on remaining scenarios for paper

---
title: "Paper Plots V1"
author: "Brett Stacy"
date: "2024-11-25"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

@@

assessment_2023_iss = tidytable(year = 1977:2023,
                                iss = c(27,
                                45,
                                54,
                                54,
                                63,
                                31,
                                117,
                                140,
                                211,
                                216,
                                396,
                                401,
                                185,
                                189,
                                1565,
                                1543,
                                913,
                                1435,
                                1561,
                                2020,
                                2142,
                                2046,
                                2722,
                                2960,
                                3140,
                                3446,
                                4301,
                                3608,
                                3455,
                                2694,
                                2115,
                                2502,
                                2218,
                                1975,
                                2596,
                                2776,
                                3293,
                                3604,
                                3324,
                                2821,
                                2469,
                                1899,
                                1367,
                                1048,
                                859,
                                1160,
                                706))
```

@@

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(2,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.3) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "red")
legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"))

plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3)

@@

legend("topleft", legend = c("boot length", "boot length + haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"), bty = "n")
```

@@

out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_24.2_ISS_200_iters_2025-02-03.RDS")

year = out_24.1$samples_1$trip_0.25$length$iss$YEAR

@@

out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_23.1_ISS_200_iters_2024-12-31.RDS")

year = out_23.1$samples_1$trip_0.25$length$iss$YEAR

@@

out_25.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_25.1_ISS_200_iters_2025-01-03.RDS")

year = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$YEAR

@@

out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.2_ISS_200_iters_2025-02-01.RDS")

>>>>

---
title: "Paper Plots V2"
author: "Brett Stacy"
date: "2024-11-25"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

@@

assessment_2023_iss = tidytable(year = 1977:2023,
                                iss = c(27,
                                45,
                                54,
                                54,
                                63,
                                31,
                                117,
                                140,
                                211,
                                216,
                                396,
                                401,
                                185,
                                189,
                                1565,
                                1543,
                                913,
                                1435,
                                1561,
                                2020,
                                2142,
                                2046,
                                2722,
                                2960,
                                3140,
                                3446,
                                4301,
                                3608,
                                3455,
                                2694,
                                2115,
                                2502,
                                2218,
                                1975,
                                2596,
                                2776,
                                3293,
                                3604,
                                3324,
                                2821,
                                2469,
                                1899,
                                1367,
                                1048,
                                859,
                                1160,
                                706))

# survey vs observer length measurements
obs_numbers = tidytable(year = 1982:2023,
                        survey = c(10863,
                        13143,
                        12133,
                        17150,
                        15872,
                        9483,
                        6950,
                        4246,
                        5428,
                        7069,
                        10129,
                        10500,
                        12931,
                        9820,
                        9348,
                        9591,
                        9574,
                        11183,
                        12170,
                        19078,
                        12365,
                        11835,
                        10986,
                        11753,
                        12530,
                        13441,
                        15328,
                        23737,
                        21223,
                        25150,
                        30177,
                        19902,
                        29204,
                        19880,
                        19507,
                        15020,
                        8806,
                        23408,
                        0,
                        17397,
                        16677,
                        19943),
                        fishery = c(9658,
                                    33200,
                                    45635,
                                    66940,
                                    58257,
                                    129226,
                                    111065,
                                    58625,
                                    39698,
                                    347227,
                                    344923,
                                    248967,
                                    359147,
                                    344794,
                                    445217,
                                    474908,
                                    438746,
                                    186233,
                                    199708,
                                    210419,
                                    230802,
                                    288854,
                                    237487,
                                    228664,
                                    179782,
                                    140663,
                                    164860,
                                    147875,
                                    131514,
                                    172269,
                                    192273,
                                    211962,
                                    234476,
                                    213888,
                                    182980,
                                    157482,
                                    124004,
                                    86800,
                                    65301,
                                    55858,
                                    73025,
                                    42942))

obs_numbers %>% 
  tidytable::summarise(sum(survey), sum(fishery))

@@

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(2,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.3) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "red")
legend(1977, 11000, lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n")
text(1977, 14000, "A")

plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3) 
text(1977, 420000, "B")

# averages
out_1.4$length$iss$iss %>% mean()
assessment_2023_iss$iss %>% mean()

@@

legend("topleft", legend = c("boot length", "boot length + haul", "boot all", "boot all + sampling strata weighting", "full"), lty = c(1,1,1,1,1), col = c("black", "blue", "orange", "green", "red"), bty = "n")

# not accounting for correlations exceed hauls?
sum((out_5.2$length$iss$iss[sub_range]-out_1.4$length$iss$nhls) < 0)

@@

out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_24.3_ISS_500_iters_2025-02-11.RDS")

year = out_24.1$samples_1$trip_0.5$length$iss$YEAR

@@

out_23.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_23.2_ISS_500_iters_2025-02-09.RDS")

year = out_23.1$samples_1$trip_0.5$length$iss$YEAR

@@

# out_25.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_25.1_ISS_200_iters_2025-01-03.RDS")
out_25.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_25.3.TAS_ISS_500_iters_2025-02-12.RDS")

# year = out_25.1$samples_1$haul_0.5_trip_0.5$length$iss$YEAR
year = out_25.1$samples_1$haul_0.5_trip_0.75$length$iss$YEAR

@@

out_18.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_18.3.TAS_ISS_500_iters_2025-02-10.RDS")
